%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/0%20-%20OCD/OCD_Chapter_04.tex $}
{$LastChangedDate: 2024-01-03 22:07:16 -0500 (Wed, 03 Jan 2024) $}
{$LastChangedRevision: 51 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: OCD_Chapter_04.tex 51 2024-01-04 03:07:16Z KneadProject $}


\chapter{Justification for and nature of changes}
\label{chap:Justification for and nature of changes}
% \input{DIDINFO_Snippets/OCD/OCD_4.0_DIDINFO.tex}

This chapter will detail why gardeners need the \ThisSystem and how it will improve the overall quality of residential garden beds.


\section{Justification for change}
\label{sec:Justification for change}
% \input{DIDINFO_Snippets/OCD/OCD_4.1_DIDINFO.tex}

Gardens need constant care during the growing season.
Any extended travel or long term time away from a garden can be detrimental from the garden's plants' health. Additionally, extreme weather brings more challenges for maintaining garden health.
Extreme heat or long periods of drought can prevent plants from reaching their full growth potential. Gardeners need a system to help mitigate these risks facing their plants.

\section{Description of needed changes}
\label{sec:Description of needed changes}
% \input{DIDINFO_Snippets/OCD/OCD_4.2_DIDINFO.tex}

Gardeners need a system that can autonomously monitor and maintain the health of their gardens. A system needs to have the capability to monitor garden health, including soil moisture, soil pH, and other factors.
The system must be able to respond to certain environmental events/thresholds (i.e. temperature, moisture levels) and activate watering systems. 
The system must be able to activate watering systems based on a set schedule. These changes will help solve the issues that are facing residential gardeners today. 

Any additional needed changes will be added to this section in the future.

\section{Priorities among the changes}
\label{sec:Priorities among the changes}
% \input{DIDINFO_Snippets/OCD/OCD_4.3_DIDINFO.tex}

A new smart residential gardening system will prioritize implementing a reliable watering system. The watering system will be able to be manually controlled, run on a set schedule, 
and respond to either preset environmental thresholds or custom thresholds that are set by the gardener.

\section{Changes considered but not included}
\label{sec:Changes considered but not included}
% \input{DIDINFO_Snippets/OCD/OCD_4.4_DIDINFO.tex}

As of now, there are no other considered changes, this section will be updated when more is known about the project.


\section{Assumptions and constraints}
\label{sec:Assumptions and constraints}
% \input{DIDINFO_Snippets/OCD/OCD_4.5_DIDINFO.tex}

Assumptions for the \ThisSystem will be added to this section when more is known about the project.
