%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/0%20-%20OCD/OCD_Chapter_06.tex $}
{$LastChangedDate: 2024-01-03 22:07:16 -0500 (Wed, 03 Jan 2024) $}
{$LastChangedRevision: 51 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: OCD_Chapter_06.tex 51 2024-01-04 03:07:16Z KneadProject $}

\chapter{Operational scenarios}
\label{chap:Operational scenarios}
% \input{DIDINFO_Snippets/OCD/OCD_6.0_DIDINFO.tex}

This chapter will detail certain operational scenarios for the \ThisSystem. Use cases will be listed below and the operational scenario will be described.


\section{Use Case: Watering Schedule}
\label{loc:UseCase1}
% \input{DIDINFO_Snippets/OCD/OCD_6.1_DIDINFO.tex}

The \ThisSystem will control it's watering system on a set schedule. By default, the watering system will be activated every 6 hours. The watering system will be active for 10 minutes and then shut off.
This process will be able to be turned off and on. Gardeners can decide if they want to set a watering schedule. The watering system will be able to be activated manually as well.


\section{Use Case: Manual Watering}
\label{loc:UseCase2}
%\input{DIDINFO_Snippets/OCD/OCD_6.1_DIDINFO.tex}

The \ThisSystem will allow gardeners to manually turn on/off the watering system. Gardeners will either toggle the system on/off. 

\section{Use Case: Environmental Watering}
\label{loc:UseCase3}

The \ThisSystem will activate it's watering system based on different environmental factors. \ThisSys will have sensors to monitor temperature, soil moisture, etc. 
Based on certain environmental thresholds, the system will toggle on/off the watering system. More information about the environmental thresholds and factors will be added to this use case later.

\section{Use Case: Future Use Cases}
\label{loc:UseCase4}
% \input{DIDINFO_Snippets/OCD/OCD_6.1_DIDINFO.tex}

At this time, there are no future use cases for the \ThisSystem.