%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/0%20-%20OCD/OCD_Chapter_05.tex $}
{$LastChangedDate: 2024-01-03 22:07:16 -0500 (Wed, 03 Jan 2024) $}
{$LastChangedRevision: 51 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: OCD_Chapter_05.tex 51 2024-01-04 03:07:16Z KneadProject $}


\chapter{Concept for a new or modified system}
\label{chap:Concept for a new or modified system}
% \input{DIDINFO_Snippets/OCD/OCD_5.0_DIDINFO.tex}

This chapter will introduce the \ThisSystem and detail it's features. 


\section{Background, objectives, and scope}
\label{sec:Background, objectives, and scope}
% \input{DIDINFO_Snippets/OCD/OCD_5.1_DIDINFO.tex}

The objective of \ThisSystem is to provide a smart gardening solution that will monitor and improve garden health for residential gardeners.
The goal for \ThisSys is to provide consistent and high quality garden care while reducing the amount of physical labor a residential gardener needs to do.


\section{Operational policies and constraints}
\label{sec:Operational policies and constraints}
% \input{DIDINFO_Snippets/OCD/OCD_5.2_DIDINFO.tex}

As of now, there are no known operational policies and constraints for the project. This section will be updated when more information is known.


\section{Description of the new or modified system}
\label{sec:Description of the new or modified system}
% \input{DIDINFO_Snippets/OCD/OCD_5.3_DIDINFO.tex}

Update section with description of new system.


\section{Users/affected personnel}
\label{sec:Users/affected personnel}
% \input{DIDINFO_Snippets/OCD/OCD_5.4_DIDINFO.tex}

The \ThisSystem will be operated by recreational gardeners. Gardeners will be able to spend less time maintaining their gardens and create
an favorable growing environment for the garden's plants. There will be clear instructions for how to setup the system and
any required materials/systems that are required for \ThisSystem to operate will be clearly stated for future users. 
Minimal training will be required to use \ThisSys. The \ThisSystem is designed to reduce a gardener's workload.


\section{Support concept}
\label{sec:Support concept}
% \input{DIDINFO_Snippets/OCD/OCD_5.5_DIDINFO.tex}

All users of \ThisSystem will be provided with clear instructions for how to setup the \ThisSystem. The instructions will include recommended configurations and layouts for how to setup \ThisSys
in a garden. Additionally, any required materials that are not included in \ThisSys will be explicitly noted. Other support information will be added in the future.

