%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/0%20-%20OCD/OCD_Chapter_03.tex $}
{$LastChangedDate: 2024-01-03 22:07:16 -0500 (Wed, 03 Jan 2024) $}
{$LastChangedRevision: 51 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: OCD_Chapter_03.tex 51 2024-01-04 03:07:16Z KneadProject $}


\chapter{Current system or situation}
\label{chap:Current System or Situation}
% \input{DIDINFO_Snippets/OCD/OCD_3.0_DIDINFO.tex}

This chapter will describe the need for the \ThisSystem and provide context for the problem it is aiming to solve.


\section{Background, objectives, and scope}
\label{sec:Background, Objectives, and Scope}
% \input{DIDINFO_Snippets/OCD/OCD_3.1_DIDINFO.tex}

Growing fruits and vegetables with consistent quality throughout the growing season is challenging for the average gardener.
It requires consistent care and nurture for a garden's plants. Plants need consistent conditions to grow and bear their best fruit.
This proves a challenge for many gardeners. Weather and temperature changes can rapidly change soil conditions. 
Additionally, gardners are not able to constantly be by their gardens. 
The \ThisSystem aims to provide gardeners with a system to aid in the monitoring of their gardens and to help maintain optimal growing conditions for their plants.

\section{Operational policies and constraints}
\label{sec:Operational Policies and Constraints}
% \input{DIDINFO_Snippets/OCD/OCD_3.2_DIDINFO.tex}

Gardeners are constrained by their availabilty and time. Maintaining a garden is a lot of work. If a gardener is on vacation or unable to tend to their garden, garden health may be compromised.


\section{Description of current system or situation}
\label{sec:Description of current system or situation}
% \input{DIDINFO_Snippets/OCD/OCD_3.3_DIDINFO.tex}

There is no current system that the \ThisSystem is trying to improve. The garden that this system will be designed to work in is a raised garden bed in a residential yard.
The garden is 8' x 4' and contains 32 cubic feet of soil.
The current process of caring for the garden involves following a set watering schedule and adjusting the schedule based on weather conditions.
There are no sprinkler systems set up in the garden. All watering is currently done manually and by a hose.
The current situation depends on a gardener being available during set watering times. Additionally, there is no way to monitor soil health other than by visual cues.
There is also no way to track the amount of water used during each watering session.


\section{Users or involved personnel}
\label{sec:Users or involved personnel}
% \input{DIDINFO_Snippets/OCD/OCD_3.4_DIDINFO.tex}

The current system relies on gardeners to manually water their gardens. Gardeners must stay up to date with their gardening schedules and monitor garden health on their own. 


\section{Support concept}
\label{sec:Support concept}
% \input{DIDINFO_Snippets/OCD/OCD_3.5_DIDINFO.tex}

There is no support for the current system.
