%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/0%20-%20OCD/OCD_Chapter_08.tex $}
{$LastChangedDate: 2024-01-03 22:07:16 -0500 (Wed, 03 Jan 2024) $}
{$LastChangedRevision: 51 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: OCD_Chapter_08.tex 51 2024-01-04 03:07:16Z KneadProject $}

\chapter{Analysis of the proposed system}
\label{chap:Analysis of the proposed system}
% \input{DIDINFO_Snippets/OCD/OCD_8.0_DIDINFO.tex}

This chapter will analize the overall advantages, disadvantages, and limitations of \ThisSystem. 

\section{Summary of advantages}
\label{sec:Summary of advantages}
% \input{DIDINFO_Snippets/OCD/OCD_8.1_DIDINFO.tex}

The \ThisSystem will have a massive impact on gardeners. Gardeners will no longer have to manually maintain their gardens. \ThisSys is an extra garden hand and will help maintain 
optimal growing conditions for plants. Garden health will also improve. \ThisSys will respond to environmental factors and keep garden conditions optimal for growing. 
Garden harvests will be more frequent, plentiful, and tastier. Overall quality of life will improve for the gardener and garden.


\section{Summary of disadvantages/limitations}
\label{sec:Summary of disadvantages/limitations}
% \input{DIDINFO_Snippets/OCD/OCD_8.2_DIDINFO.tex}

Plants do not all grow in the same conditions. The \ThisSystem will be configured to maintain a garden in a specific climate zone. The garden may have plants that grow best in a different climate zone
or have plants from multiple climate zones. The \ThisSystem will not be configured to maintain a garden with plants from multiple climate zones. \ThisSys assumes that all plants within the garden grow in similar conditions.


\section{Alternatives and trade-offs considered}
\label{sec:Alternatives and trade-offs considered}
\input{DIDINFO_Snippets/OCD/OCD_8.3_DIDINFO.tex}

No alternatives have been considered at this time, this section will be updated in the future.
