%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/6a%20-%20STP/STP_Chapter_03.tex $}
{$LastChangedDate: 2023-12-24 21:32:44 -0500 (Sun, 24 Dec 2023) $}
{$LastChangedRevision: 32 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: STP_Chapter_03.tex 32 2023-12-25 02:32:44Z KneadProject $}

% \input{DIDINFO_Snippets/STP/STP_4.2.0_DIDINFO.tex}

This section defines the plans for the \TestIdName\xspace test.

\subsubsection{Test Objective}
\label{loc:TestObjective\TestIdName}

The test objective for \TestIdName\xspace is to validate that the Raspberry Pi Pico W is connected to the internet.

\subsubsection{Test Level}
\label{loc:TestLevels\TestIdName}

The test level for \TestIdName\xspace is a system level test.

\subsubsection{Test Type or Class}
\label{loc:TestLevels\TestIdName}

The test type or class for \TestIdName\xspace is a connection test.

\subsubsection{Qualification Method}
\label{loc:TestQualificationMethod\TestIdName}

The test qualification method for \TestIdName\xspace is the successful reading of packets. The test will compare the number of packets sent with the number of packets received.

\subsubsection{Traceability}
\label{loc:TestTraceability\TestIdName}

% The test traceability for \TestIdName\xspace is \TBD.
There is no test traceability for \TestIdName\xspace.

\subsubsection{Special Requirements}
\label{loc:TestSpecialRequirements\TestIdName}

% The test special requirements for \TestIdName\xspace are \TBD.
There are no special requirements for \TestIdName\xspace.

\subsubsection{Data Recoding}
\label{loc:TestDataRecoding\TestIdName}

The test data recoding for \TestIdName\xspace will be the packets sent and packets received.

\subsubsection{Assumptions or Constraints}
\label{loc:TestAssumptionsOrConstraints\TestIdName}

The test assumptions or constraints for \TestIdName\xspace are that the tester has access to a WiFi network.

\subsubsection{Safety, Security, and Privacy}
\label{loc:TestSafetySecurityPrivacy\TestIdName}

% The test safety, security, and privacy for \TestIdName\xspace are \TBD.
There are no test safety, security, or privacy concerns for \TestIdName\xspace.
