%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/6a%20-%20STP/STP_Chapter_03.tex $}
{$LastChangedDate: 2023-12-24 21:32:44 -0500 (Sun, 24 Dec 2023) $}
{$LastChangedRevision: 32 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: STP_Chapter_03.tex 32 2023-12-25 02:32:44Z KneadProject $}

% \input{DIDINFO_Snippets/STP/STP_3.x.0_DIDINFO.tex}

This section identifies and describes the \TestEnvName\xspace test environment. This test environment will verify and validate that the Raspberry Pi Pico W has successfully connected to the internet.

\subsection{Software Items}
\label{loc:Software\TestEnvName}
\input{DIDINFO_Snippets/STP/STP_3.x.1_DIDINFO.tex}

The software items needed for the \TestEnvName\xspace Test Environment are a Python script that opens a socket and sends data packets to a device connected to the internet.


\subsection{Hardware and Firmware Items}
\label{loc:Hardware\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.2_DIDINFO.tex}

The hardware and firmware items needed for the \TestEnvName\xspace Test Environment are a Raspberry Pi Pico W that has been configured to connect to the internet.


\subsection{Other Materials}
\label{loc:OtherMaterials\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.3_DIDINFO.tex}

There are no other materials needed of the \TestEnvName.


% \subsection{Proprietary Nature}
% \label{loc:ProprietaryNature\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.4_DIDINFO.tex}

% The proprietary nature, acquirer’s rights, and licensing issues for the \TestEnvName\xspace Test Environment are \TBD.


\subsection{Installation}
\label{loc:Installation\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.5_DIDINFO.tex}

The installation steps required for the \TestEnvName\xspace Test Environment are:

\begin{itemize}
    \item Installing a WiFi connection script on the Raspberry Pi Pico W.
    \item Running the Python script to send packets across the WiFi network.
\end{itemize}


% \subsection{Participating Organizations}
% \label{loc:Organizations\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.6_DIDINFO.tex}

% The participating organizations for the \TestEnvName\xspace Test Environment are \TBD.


\subsection{Personnel}
\label{loc:Personnel\TestEnvName}
\input{DIDINFO_Snippets/STP/STP_3.x.7_DIDINFO.tex}

The personnel planning for the \TestEnvName\xspace Test Environment is the user of the Raspberry Pi Pico W.


\subsection{Orientation Planning}
\label{loc:Orientation\TestEnvName}
\input{DIDINFO_Snippets/STP/STP_3.x.8_DIDINFO.tex}

The orientation planning for the \TestEnvName\xspace Test Environment is that the tester must know the WiFi SSID and password for the WiFi network. 
Additionally, the tester must know the IP address for the Raspberry Pi Pico W.


\subsection{Tests to be Performed}
\label{loc:Tests\TestEnvName}
\input{DIDINFO_Snippets/STP/STP_3.x.9_DIDINFO.tex}

The tests to be performed for the \TestEnvName\xspace Test Environment will be a WiFi packet test.%reference section 4
A socket will be opened and packets will be sent across the network to a specified IP address. The IP address must be the IP address for the Raspberry Pi Pico W.

