%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/6a%20-%20STP/STP_Chapter_03.tex $}
{$LastChangedDate: 2023-12-24 21:32:44 -0500 (Sun, 24 Dec 2023) $}
{$LastChangedRevision: 32 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: STP_Chapter_03.tex 32 2023-12-25 02:32:44Z KneadProject $}

% \input{DIDINFO_Snippets/STP/STP_3.x.0_DIDINFO.tex}

This section identifies and describes the \TestEnvName\xspace test environment. This test environment will verify and validate that the \ThisSystem successfully activates the \ThisSys irrigation system during active watering mode.

\subsection{Software Items}
\label{loc:Software\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.1_DIDINFO.tex}

There are no software items for this test.


\subsection{Hardware and Firmware Items}
\label{loc:Hardware\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.2_DIDINFO.tex}

The hardware items needed for the \TestEnvName\xspace Test Environment are a water pump, temperature sensor, soil moisture sensor, and a \RaspPi.
The firmware items needed for the \TestEnvName\xspace Test Environment is firmware that monitors the temperature and soil moisture data and triggers the water pump once environmental thresholds have been met.


\subsection{Other Materials}
\label{loc:OtherMaterials\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.3_DIDINFO.tex}

There are no other materials needed of the \TestEnvName.


% \subsection{Proprietary Nature}
% \label{loc:ProprietaryNature\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.4_DIDINFO.tex}

% The proprietary nature, acquirer’s rights, and licensing issues for the \TestEnvName\xspace Test Environment are \TBD.


\subsection{Installation}
\label{loc:Installation\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.5_DIDINFO.tex}

There are no installation steps for this test.


\subsection{Participating Organizations}
\label{loc:Organizations\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.6_DIDINFO.tex}

There are no participating organizations for the \TestEnvName\xspace test.


\subsection{Personnel}
\label{loc:Personnel\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.7_DIDINFO.tex}

There are no personnel requirements for the \TestEnvName\xspace test.


\subsection{Orientation Planning}
\label{loc:Orientation\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.8_DIDINFO.tex}

There are no orientation planning requirements for the \TestEnvName\xspace test.


\subsection{Tests to be Performed}
\label{loc:Tests\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.9_DIDINFO.tex}

The tests to be performed for the \TestEnvName\xspace Test Environment will be to ensure that the temperature and soil moisture sensors operate properly. 
Once the temperature has crossed the environmental threshold for 5-minutes, \ThisSys will activate the irrigation system.
Once the soil moisture levels have crossed the environmental threshold for 5-minutes, \ThisSys will activate the irrigation system.


