%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/6a%20-%20STP/STP_Chapter_03.tex $}
{$LastChangedDate: 2023-12-24 21:32:44 -0500 (Sun, 24 Dec 2023) $}
{$LastChangedRevision: 32 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: STP_Chapter_03.tex 32 2023-12-25 02:32:44Z KneadProject $}

% \input{DIDINFO_Snippets/STP/STP_3.x.0_DIDINFO.tex}

This section identifies and describes the \TestEnvName\xspace test environment. This test environment will verify and validate that the \ThisSystem meets the IP65 waterproofing requirements.

\subsection{Software Items}
\label{loc:Software\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.1_DIDINFO.tex}

There are no software items for this test.


\subsection{Hardware and Firmware Items}
\label{loc:Hardware\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.2_DIDINFO.tex}

The hardware items needed for the \TestEnvName\xspace Test Environment are the external casings for the \ThisSystem and it's sensors. There are no firmware items needed for this test.


\subsection{Other Materials}
\label{loc:OtherMaterials\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.3_DIDINFO.tex}

There are no other materials needed of the \TestEnvName.


% \subsection{Proprietary Nature}
% \label{loc:ProprietaryNature\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.4_DIDINFO.tex}

% The proprietary nature, acquirer’s rights, and licensing issues for the \TestEnvName\xspace Test Environment are \TBD.


\subsection{Installation}
\label{loc:Installation\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.5_DIDINFO.tex}

There are no installation steps for this test.


\subsection{Participating Organizations}
\label{loc:Organizations\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.6_DIDINFO.tex}

The participating organizations for the \TestEnvName\xspace waterproofing test is VTEC Laboratories.


\subsection{Personnel}
\label{loc:Personnel\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.7_DIDINFO.tex}

There are no personnel requirements for the \TestEnvName\xspace test.


\subsection{Orientation Planning}
\label{loc:Orientation\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.8_DIDINFO.tex}

There are no orientation planning requirements for the \TestEnvName\xspace test.


\subsection{Tests to be Performed}
\label{loc:Tests\TestEnvName}
% \input{DIDINFO_Snippets/STP/STP_3.x.9_DIDINFO.tex}

The tests to be performed for the \TestEnvName\xspace Test Environment will be waterproofing test to ensure that the external housing for the \ThisSystem meet the minimum IP65 waterproof rating.
VTEC Laboratories will perform the waterproofing test.

