%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/7%20-%20SVD/SVD_Chapter_03.tex $}
{$LastChangedDate: 2023-12-26 12:10:35 -0500 (Tue, 26 Dec 2023) $}
{$LastChangedRevision: 42 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: SVD_Chapter_03.tex 42 2023-12-26 17:10:35Z KneadProject $}


\chapter{Version Description}
\label{loc:VersionDescription}
% \input{DIDINFO_Snippets/SVD/SVD_3.0.0_DIDINFO.tex}

This chapter will provide an inventory of all used software and hardware, provide change information for the \ThisSystem, and provide installation instructions for required software.

\section{Inventory of Materials}
\label{loc:InventoryOfMaterials}
% \input{DIDINFO_Snippets/SVD/SVD_3.1.0_DIDINFO.tex}

The materials used for the \ThisSystem are:

\begin{itemize}
    \item Raspberry Pi Pico W
    \begin{itemize}
        \item \href{https://datasheets.raspberrypi.com/picow/pico-w-datasheet.pdf}{Raspberry Pi Pico W Datasheet}
    \end{itemize}
\end{itemize}

The Raspberry Pi Pico W is a RP2040-based microcontroller board with wireless capabilities.

\section{Inventory of Software}
\label{loc:InventoryOfSoftware}
% \input{DIDINFO_Snippets/SVD/SVD_3.2.0_DIDINFO.tex}

The software used for the \ThisSystem are:

\begin{itemize}
    \item pico-sdk: Release SDK 1.5.1 June 13, 2023
    \begin{itemize}
        \item \href{https://github.com/raspberrypi/pico-sdk}{pico-sdk Github repository}
    \end{itemize}
    \item pico-examples: Release Tag sdk-1.5.1 June 11, 2023
    \begin{itemize}
        \item \href{https://github.com/raspberrypi/pico-examples}{pico-examples Github repository}
    \end{itemize}
\end{itemize}

Both the pico-sdk and pico-examples repositories are provided by the Raspberry Pi Ltd organization. 
The pico-sdk and pico-examples repositories work on any Raspberry Pi Pico board.

The pico-sdk SDK is a C/C++ SDK designed for the Raspberry Pi Pico family of microcontroller boards. The documentation for pico-sdk can be found in the SDK documentation \cite{ref__RP_Pico_C_SDK}.
The pico-examples repository contains sample code and projects that are provided by the Raspberry Pi Ltd organization. The sample projects use Release 1.5.1 of the pico-sdk. 

% \section{Changes From Prior Version}
% \label{loc:ChangesFromPriorVersion}
% \input{DIDINFO_Snippets/SVD/SVD_3.3.0_DIDINFO.tex}

% This section is \TBD. (And is not applicable to the first release.)


\section{Adaptation Data}
\label{loc:AdaptationData}
% \input{DIDINFO_Snippets/SVD/SVD_3.4.0_DIDINFO.tex}

There is currently no unique-to-site data for the \ThisSystem. Updates will be made to this section when applicable.


\section{Related (Third Party) Documents}
\label{loc:RelatedDocuments}
% \input{DIDINFO_Snippets/SVD/SVD_3.5.0_DIDINFO.tex}

The following is a list of third party documents associated with the software used for the \ThisSystem:

\begin{itemize}
    \item \cite{ref__RP_Getting_Started} Raspberry Pi Pico Getting Started Guide
    \item \cite{ref__RP_Pico_C_SDK} Raspberry Pi Pico C/C++ SDK Official Documentation
\end{itemize}


\section{Installation Instructions}
\label{loc:InstallationInstructions}
% \input{DIDINFO_Snippets/SVD/SVD_3.6.0_DIDINFO.tex}

This section will provide an overview for how to install the pico-sdk and pico-examples repositories.

\subsection{Installing pico-sdk}
For detailed steps on how to install the pico-sdk, please refer to the \cite{ref__RP_Getting_Started} Raspberry Pi Pico Getting Started Guide. 
The pico-sdk can be found in the github repo: \url{github.com/raspberrypi/pico-sdk}
The following will list the necessary steps to install the pico-sdk:

\begin{enumerate}
    \item Install CMake (at least version 3.13), and GCC cross compiler
    \item Clone the Raspberry Pi Pico SDK repository using git clone
    \item Set the ENV variable PICO\textunderscore SDK\textunderscore PATH to the SDK location in your environment.
    \item Setup a CMakeLists.txt file
\end{enumerate}

These steps will install and configure the pico-sdk repository onto your system.

\subsection{Installing pico-examples}
For detailed steps on how to install the pico-examples, please refer to the \cite{ref__RP_Getting_Started} Raspberry Pi Pico Getting Started Guide. 
pico-examples can be found in the github repo: \url{github.com/raspberrypi/pico-examples}
The following will list the necessary steps to install the pico-examples:

\begin{enumerate}
    \item Clone the Raspberry Pi Pico Examples repository using git clone
\end{enumerate}

\subsection{Quick Pico Setup via Install Script}
The Raspberry Pi organization provides a setup shell script to configure your system with the pico-sdk and pico-examples script. 
The Getting Started With Pico \cite{ref__RP_Getting_Started} guide provides more information about the setup script.
The following are the necessary steps to run the install script:

\begin{enumerate}
    \item Get the script via terminal command: wget \url{https://raw.githubusercontent.com/raspberrypi/pico-setup/master/pico_setup.sh}
    \item Make the script executable with: chmod +x pico\textunderscore setup.sh
    \item Run the script with: ./pico\textunderscore setup.sh
\end{enumerate}

\section{Possible Problems and Known Errors}
\label{loc:PossibleProblemsAndKnownErrors}
% \input{DIDINFO_Snippets/SVD/SVD_3.7.0_DIDINFO.tex}

There are no possible problems or known errors at this time. This section will be updated if and when applicable.
