\subsection{Contents and Structure}
\label{loc:DocOverview_ContentsAndStructure}

This document format is based upon the guidance in the \SDP \DID~\cite{ref__SVD_DID}, but is tailored to reflect current quality management system (\QMS) requirements for many of the items described in the \DID.
The system development plan information also follows the guidelines of ISO-12207~\cite{ref__ISO_12207} and MIL-STD-498~\cite{ref__MIL_STD_498} (from which ISO-12207 originated).
It is expected that significant coverage of the \SDP \DID items will simply be references to external \QMS or \CMMI documentation.
Thus, agencies using this artifact will formalize it to serve as a checklist for tailoring each effort per their own processes and procedures.

This tailoring also includes planning for hardware aspects as may be needed for the complete system development efforts.
The \SDP \DID mainly covered integration of software onto hardware.
This artifact includes sections that cover the development of hardware as well as development of the software.
Integration and testing are also included.
But, as noted above, all apsects of development are expected to illustrate the existing \QMS steps to be followed based on organizational processes and the project's operational needs.

This document follows a tailored \SVD sub-section order of:
\begin{description}[itemindent=5pt,topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
	\item[Section 1] provides an overview of the system and this document.
	\item[Section 2] lists general and application-specific reference documents as well as glossary terms and acronyms. 
	\item[Section 3] summarizes the required work, with references to existing \QMS processes and procedures as applicable:
	\begin{itemize}[topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
		\item program status / acquisition strategy,
		\item \SDLC Situation,
		\item plans for development of requirement artifacts,
		\item plans for overall documentation development,
		\item schedule / resource constraints, and
		\item other requirements/constraints.
	\end{itemize}
	\item[Section 4] Plans for system development
		\begin{itemize}[topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
			\item Hardware development processes and plans,
			\item Firmware development processes and plans,
			\item Software development processes and plans,
			\item Integration plans,
			\item Testing plans, and
			\item Other development activities per organizational processes.
		\end{itemize}
		\item[Section 5] Plans for system transistion
		\begin{itemize}[topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
			\item Configuration Management plans,
			\item Release plans,
			\item User Support plans, and
			\item Other system transition activities per organizational processes.
		\end{itemize}
	\item[Section 6] Management and control activities
		\begin{itemize}[topsep=0pt,itemsep=0pt,partopsep=0pt, parsep=0pt]
			\item SETR events (internal previews and with customer),
			\item Skills and resources needed,
			\item Schedule Development and Monitoring, and
			\item Other management and control activities per organizational processes.
		\end{itemize}
	\item[Section 7] if needed, lists any general notes as may be applicable.
	\item[Appendices] if needed, provide additional information as may be needed.
\end{description}

\input{DIDINFO_Snippets/DIDINFOoverview.tex}
