%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/0%20-%20SDP/SDP_Chapter_04.tex $}
{$LastChangedDate: 2023-12-24 20:45:24 -0500 (Sun, 24 Dec 2023) $}
{$LastChangedRevision: 27 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: SDP_Chapter_04.tex 27 2023-12-25 01:45:24Z KneadProject $}


\chapter{System Development Plans}
\label{loc:PlansForSystemDevelopment}
% \input{DIDINFO_Snippets/SDP/SDP_4.0.0_DIDINFO.tex}

This chapter will provide a brief overview of the required hardware and firmware for \ThisSystem. 

\section{Hardware Development Plans}
\label{loc:SDP_HardwareDevelopmentPlans}
% \input{DIDINFO_Snippets/SDP/SDP_4.1.0_DIDINFO.tex}

There will be no hardware development for this project. All development will take place on a Raspberry Pi Pico W development kit.

\section{Firmware Development Plans}
\label{loc:SDP_FirmwareDevelopmentPlans}
% \input{DIDINFO_Snippets/SDP/SDP_4.2.0_DIDINFO.tex}

The firmware development plan will follow the development assignment outline for the course ENPM818I.
The development assignments are as follows:

\begin{itemize}
    \item Dev Assignment 1
    \begin{itemize}
        \item Development kit and tools are operational
    \end{itemize}
    \item Dev Assignment 2
    \begin{itemize}
        \item Debugger and Emulator tools for the devlopment kit are operational
    \end{itemize}
    \item Dev Assignment 3
    \begin{itemize}
        \item Demonstrate necessary IO Stream and Interrupt Handler for the project.
    \end{itemize}
    \item Dev Assignment 4
    \begin{itemize}
        \item Demonstrate security measures necessary for the project.
    \end{itemize}
    \item Dev Assignment 5
    \begin{itemize}
        \item Implement networking capabilities for the project.
    \end{itemize}
\end{itemize}

\section{Software Development Plans}
\label{loc:SDP_SoftwareDevelopmentPlans}
% \input{DIDINFO_Snippets/SDP/SDP_4.3.0_DIDINFO.tex}

\subsection{Raspberry Pi Pico C/C++ SDK Overview + Installation}

The main documentation for the Raspberry Pi Pico C/C++ SDK can be found in \citePicoSDK. 
The document provides information about the SDK architecture, Programmable I/O, and Library documentation. 

Installation instructions can be found in \citePicoGetStart. Chapter 1 of the Getting Started guide provides instructions for how to setup the Raspberry Pi Pico using the \href{https://raw.githubusercontent.com/raspberrypi/pico-setup/master/pico_setup.sh}{pico\textunderscore setup} script.
Chapter 2 of the Getting Started guide provides instructions for how to build, install, and work with the C/C++ SDK. 

\subsubsection{Setting Up the Raspberry Pi Pico}
To setup a Raspberry Pi Pico, follow chapter 1 of \citePicoGetStart. Use the \href{https://raw.githubusercontent.com/raspberrypi/pico-setup/master/pico_setup.sh}{pico\textunderscore setup.sh} installation script. 
This installation script will:
\begin{itemize}
    \item Create a directory called pico
    \item Install required dependencies
    \item Download the pico-sdk, pico-examples, pico-extras, and pico-playground repositories
    \item Define ENV variable paths in the .bashrc file.
    \item Build the blink and hello\textunderscore world examples in pico-examples/build/blink and pico-examples/build/hello\textunderscore world
    \item Download and build picotool, and copy it to /usr/local/bin.
    \item Download and build picoprobe.
    \item Download and install Visual Studio Code
    \item Download and compile OpenOCD
    \item Install the required Visual Studio Code extensions
    \item Configure the Raspberry Pi UART for use with Raspberry Pi Pico
\end{itemize}

\subsubsection{Installing the Raspberry Pi Pico C/C++ SDK}
To install the Raspberry Pi Pico C/C++ SDK, follow chapter 2 of \citePicoGetStart. Section 2.1 instructs to install the SDK from the \href{https://github.com/raspberrypi/pico-sdk}{pico-sdk github repository}.
It also links to the \href{https://github.com/raspberrypi/pico-examples}{pico-examples github repository} that provides a set of example applications that are written using the C/C++ SDK.
Additionally, in sections 2.2 and 2.3, there are installation instructions for required tools to build and run applications in \href{https://github.com/raspberrypi/pico-examples}{pico-examples} and information for how to update the SDK. The tools include:

\begin{itemize}
    \item gcc-arm-none-eabi
    \item libnewlib-arm-none-eabi
    \item build-essential
\end{itemize}



The software development plan for this project is still \TBD. This section will be updated in the future.


\section{Integration Plans}
\label{loc:SDP_IntegrationPlans}
% \input{DIDINFO_Snippets/SDP/SDP_4.4.0_DIDINFO.tex}

The integration plans for this project are still \TBD. This section will be updated in the future.


\section{Testing Plans}
\label{loc:SDP_TestingPlans}
% \input{DIDINFO_Snippets/SDP/SDP_4.5.0_DIDINFO.tex}

All firmware and software for \ThisSystem will be accompanied with unit tests. 
An open source tool will be selected to audit the code base and there will be a set threshold for code coverage. 
Otherwise, the formal testing plan for \ThisSystem is still \TBD and will be updated in the future.


\section{Other Development Activities}
\label{loc:SDP_OtherDevelopmentActivities}
% \input{DIDINFO_Snippets/SDP/SDP_4.6.0_DIDINFO.tex}

Other development activities will be added to this document in the future. As of now, this section is \TBD.