%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/0%20-%20SDP/SDP_Chapter_05.tex $}
{$LastChangedDate: 2023-12-24 20:45:24 -0500 (Sun, 24 Dec 2023) $}
{$LastChangedRevision: 27 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: SDP_Chapter_05.tex 27 2023-12-25 01:45:24Z KneadProject $}


\chapter{System Transition Plans}
\label{loc:RequiredWork}
% \input{DIDINFO_Snippets/SDP/SDP_5.0.0_DIDINFO.tex}

The following chapter details the system transition plans for \ThisSystem. 

\section{Configuration Management Plans}
\label{loc:STP_ConfigMngtPlans}
% \input{DIDINFO_Snippets/SDP/SDP_5.1.0_DIDINFO.tex}

All code repositories for \ThisSystem will be housed in Github. All code repositories will be controlled by Git.

New code will be added and integrated into the \ThisSystem code base on a feature by feature basis. 
Pull Requests will be subject to a specified template, minimum code test coverage threshold met, and passing of other specified tests. 
Any PRs that fail to meet the template specifications and testing requirements will be rejected until the requirements are met.
A PR template, code coverage threshold, and required tests will be detailed in the future.



\section{Release Plans}
\label{loc:STP_ReleasePlans}
% \input{DIDINFO_Snippets/SDP/SDP_5.2.0_DIDINFO.tex}

Release plans for \ThisSystem are still \TBD. As of now, there are no plans for a broad commercial release.

\section{User Support Plans}
\label{loc:STP_UserSupportPlans}
% \input{DIDINFO_Snippets/SDP/SDP_5.3.0_DIDINFO.tex}

User Support Plans for \ThisSystem are still \TBD. This section will be updated once there are commercial release plans..


\section{Other Transition Plans}
\label{loc:STP_OtherTransitionPlans}
% \input{DIDINFO_Snippets/SDP/SDP_5.4.0_DIDINFO.tex}

Other transition plans for \ThisSystem are still \TBD. This section will be updated in the future.