%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/0%20-%20SDP/SDP_Chapter_06.tex $}
{$LastChangedDate: 2023-12-24 20:45:24 -0500 (Sun, 24 Dec 2023) $}
{$LastChangedRevision: 27 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: SDP_Chapter_06.tex 27 2023-12-25 01:45:24Z KneadProject $}

\chapter{Management and Control Activities}
\label{loc:MngtContrlActivities}
% \input{DIDINFO_Snippets/SDP/SDP_6.0.0_DIDINFO.tex}

This chapter will cover the technical reviews, skills and resources, and scheduled development and monitoring activitis for the \ThisSystem project.

\section{Technical Review Events}
\label{loc:MCA_TechReviewEvents}
% \input{DIDINFO_Snippets/SDP/SDP_6.1.0_DIDINFO.tex}

The technical review events for the \ThisSystem project will be the design assignments throughout ENPM818I.

The design assignments are as follows:
\begin{itemize}
    \item Design Assignment 1
    \begin{itemize}
        \item Create drafts for the \SDP and \SVD artifacts.
    \end{itemize}
    \item Design Assignment 2
    \begin{itemize}
        \item Create drafts for the \OCD and \SPS artifacts.
    \end{itemize}
    \item Design Assignment 3
    \begin{itemize}
        \item Create drafts for the \SSS artifact.
    \end{itemize}
    \item Design Assignment 4
    \begin{itemize}
        \item Create drafts for the \SSDD artifact.
    \end{itemize}
    \item Design Assignment 5
    \begin{itemize}
        \item Create drafts for the \STP and \STS artifacts.
    \end{itemize}
\end{itemize}

The artifacts for each design assignment are expected to include pertinent information for the \ThisSystem project and specifics to the corresponding development assignment it's paired with.

\section{Skills and Resources Needed}
\label{loc:MCA_SkillsResourcesNeeded}
% \input{DIDINFO_Snippets/SDP/SDP_6.2.0_DIDINFO.tex}

As of now, it is unknown what skills and resources will be needed for the \ThisSystem project. This section is still \TBD and will be updated when more information is available.


\section{Scheduled Development and Monitoring}
\label{loc:MCA_ScheduleDevMonitoring}
% \input{DIDINFO_Snippets/SDP/SDP_6.3.0_DIDINFO.tex}

The schedule development and monitoring for the \ThisSystem project is currently unknown. This section is still \TBD and will be updated when more information is available.


\section{Other Management and Control Activities}
\label{loc:MCA_OtherActivities}
% \input{DIDINFO_Snippets/SDP/SDP_6.4.0_DIDINFO.tex}

Other management and control activities for the \ThisSystem project is currently unknown. This section is still \TBD and will be updated when more information is available.