%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/1%20-%20SDP/SDP_Chapter_03.tex $}
{$LastChangedDate: 2023-12-27 21:52:08 -0500 (Wed, 27 Dec 2023) $}
{$LastChangedRevision: 44 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: SDP_Chapter_03.tex 44 2023-12-28 02:52:08Z KneadProject $}


\chapter{Required Work Overview}
\label{loc:RequiredWorkOverview}


This chapter will provide and overview of the required work, project constraints, project status, and project dependencies for the \ThisSystem. 

\section{Program Status}
\label{loc:RWO_ProgramStatus}
% \input{DIDINFO_Snippets/SDP/SDP_3.1.0_DIDINFO.tex}

The \ThisSystem program exists within the \UMD \MAGE class ENPM818I: Variable Topics in Engineering: Embedded Software Design and Optimization
under the supervision of Dr. W. Lewis Collier.


\section{SDLC Situation}
\label{loc:RWO_SDLC}
% \input{DIDINFO_Snippets/SDP/SDP_3.1.0_DIDINFO.tex}

This is an original project. All materials for this project are generated for the purpose of designing the \ThisSystem. Design materials will be completed by the end of ENPM818I.


\section{Requirement Plans}
\label{loc:RWO_RequirementPlans}
% \input{DIDINFO_Snippets/SDP/SDP_3.2.0_DIDINFO.tex}

The requirement plan for the \ThisSystem project is to design and document the design plan for the \ThisSystem.  


\section{Documentation Plans}
\label{loc:RWO_DocumentationPlans}
% \input{DIDINFO_Snippets/SDP/SDP_3.3.0_DIDINFO.tex}

The documents listed 

The following documents are listed here just to test reference generation.
A ``real'' \SDP would reference these as applicable for the project.
\begin{itemize}
	\item \citeExProjOCD is the \OCD, which outlines the project overall so, generally, it is created first.
	\item \citeExProjSDP is this document.
	\item \citeExProjSPS is the \SPS, which should come from the customer or end user, but often is generated by the developer with customer approval.
	\item \citeExProjSSS is the \SSS that is the developer's design specification to meet the \SPS requirements.
	\item \citeExProjSUM is the \SUM that acts somewhat like part of the \SSS since it illustrates the \UI design part of the \SSS, but in a separate artifact that also can be used as a standalone users' manual.
	\item \citeExProjHRS is a \HRS, which often is not used for smaller projects but can have multiple instances for large projects to more fully detail hardware design.	
	\item \citeExProjSRS is a \SRS, which often is not used for smaller projects but can have multiple instances for large projects to more fully detail software or firmware design.
	\item \citeExProjIRS is the \IRS, which often is not use but may be needed, even if \HRS or \SRS artifacts are not, to fully document detailed interfaces such as Application Programming Interfaces (\APIs) or other detailed mechanical or electrical interfaces.
	\item \citeExProjSSDD is the \SSDD that provides a road map to the design and other design details needed to understand the hardware and software design.
	\item \citeExProjSTP is the \STP that highlights the planning for system testing.
	\item \citeExProjSTS is the \STS, which is sometimes called a test procedure. There could be multiple of these based on the overall project size.
	\item \citeExProjSTR is an \STR that documents the results of a given test. Multiple instances are expected based on the test plan. And, there could be multiple versions of a given test plan to document repeated occurrences of a given test specification/procedure.
	\item \citeExProjSVD is an \SVD that documents a given release of a system. Multiple versions of these ``release notes'' are expected, with one \SVD issued for each system release cycle.

\end{itemize}



\section{Schedule and Resource Constraints}
\label{loc:RWO_ScheduleAndResourceConstraints}
% \input{DIDINFO_Snippets/SDP/SDP_3.4.0_DIDINFO.tex}

The \ENPM course and \ThisSystem project involves five development milestones and five design milestones.
The development assignments must demonstrate understanding of the stated embedded development objectives. 
The design assignments require draft completions of the listed artifacts and that will be the basis of the design artifacts for the final project.
The following is the order in which assignments must be completed for this course and project.

\begin{itemize}
	\item Development Assignment 1: Dev Kit and Tools
	\item Design Artifact 1: \SDP and \SVD
	\item Development Assignment 2: Debugger and Emulator
	\item Design Artifact 2: \OCD and \SPS
	\item Development Assignment 3: IO Streams and Interrupts
	\item Design Artifact 3: \SSS
	\item Development Assignment 4: Security Measures
	\item Design Artifact 4: \SSDD
	\item Development Assignment 5: Networking
	\item Design Artifact 5: \STP and \STS
\end{itemize}

There are currently no known resource constraints. This project is only designed by one person. Design work is the culmination of my work throughout the class.

\section{Other Constraints}
\label{loc:RWO_OtherConstraints}
% \input{DIDINFO_Snippets/SDP/SDP_3.5.0_DIDINFO.tex}

Current constraints for the \ThisSystem project are unknown. As design and development of the \ThisSystem project progresses, this section will be updated.