The control requirements for \ThisSystem are listed below.

%%% \ONERQMTV[9] is macro for consistently formatted requirements
\ONERQMTVKPP
% #1 is requirement Number
{\RqtNumberBase.1}
% #2 is Title
{Water Pump Control}
% #3 is requirement label (expected to be of form rqt:XXX)
{rqt:ControlOne}
% #4 is Text of the specification
{All \ThisSys variants shall be capable of activating and deactivating a US Solar Pump B3A 5V PWM Circulating water pump.}
% #5 is Status (S in {(T), (O), (I), (D)} listed by phase as \item [] S)
{
	\item [All Phases] Threshold
}
% #6 is Acceptance
{This requirement shall be verified by demonstration.}
% #7 is Traceability
{
	\item [N/A] This requirement is a base requirement.
}
% #8 is Notes; listed as enumeration \item ...
{
  \item The \ThisSystem will be activate/deactivate a US Solar Pump B3A 5V PWM Circulating water pump based on environmental data meeting thresholds or set time durations have passed.
  \item \href{https://www.ussolarpumps.com/catalog/5v-pwm-wired-pumps/b3a-5v-pwm-circulating-pump/}{US Solar Pump B3A 5V PWM Circulating Water Pump Product Page}
}
% #9 is changebar version
{P1}
%%%%% end \ONERQMTV[9] macro

%%% \ONERQMTV[9] is macro for consistently formatted requirements
\ONERQMTVKPP
% #1 is requirement Number
{\RqtNumberBase.2}
% #2 is Title
{Irrigation Mode Switching}
% #3 is requirement label (expected to be of form rqt:XXX)
{rqt:ControlTwo}
% #4 is Text of the specification
{All \ThisSys variants shall be capable of switching it's active system mode via the GPIO button interface.}
% #5 is Status (S in {(T), (O), (I), (D)} listed by phase as \item [] S)
{
	\item [All Phases] Threshold
}
% #6 is Acceptance
{This requirement shall be verified by demonstration.}
% #7 is Traceability
{
	\item [N/A] This requirement is a base requirement.
}
% #8 is Notes; listed as enumeration \item ...
{
  \item The irrigation system mode will be able to change between Active Monitoring, Scheduled Irrigation, and Manual Activation.
}
% #9 is changebar version
{P1}
%%%%% end \ONERQMTV[9] macro