%%% SVN stuff
\svnidlong
{$HeadURL: https://192.168.1.5/svn/NASC/_Projects/DRAGON-EYE/SystemDocuments/zSystemWideData/TestPrepProcs/TestCase_BuildSoftware.tex $}
{$LastChangedDate: 2016-09-12 21:24:52 -0400 (Mon, 12 Sep 2016) $}
{$LastChangedRevision: 341 $}
{$LastChangedBy: LCollier $}
\svnid{$Id: TestCase_BuildSoftware.tex 341 2016-09-13 01:24:52Z LCollier $}

\TestProcedure  %\TestProcedure[6] test description container
% #1 is the test description number, usually built from section number + description within the section
{\TestProcNumber.1}
% #2 is the test description name
{\StdTestNameX Build Software}
% #3 is the test description LaTeX label
{lab:tproc_\StdTestName_BuildSoftware_\TestProcNumber}
% #4 is the list of requirements covered by this test
{
\tpRqmt{3.10.2.1}%Linux support
\tpRqmt{3.10.2.2}%Windows support
}
% #5 is the list of test steps
{
\tpStep{Record the operating system(s) supported by this software.}{Supported operating systems are recorded.}{12pt}
\tpStep{Verify that all source files, build files, and instructions are supplied for all supported operating systems.}{Names of files for makefiles, project files, and build instructions for supported operating systems are recorded.}{36pt}
\tpStep{Follow the instructions supplied for all supported operating systems to build the software.}{Following build instructions  produces a library to be used with the bridge code and executable test driver program(s) with no errors or warnings for all supported operating systems.}{24pt}
\tpStep{Verify that the executable test driver program(s) generated for all supported operating systems run.}{The executable program(s) is(are) listed and run under the associated operating systems.}{36pt}
}
% #6 is the list notes
{
\tpNote{The goal of this test case is to verify that the build instructions for all executable code result in operational code; this does not check the validity of the operations of the code.}
\tpNote{The names of the source code do not need to be recorded here since the makefile and/or project file contains this information.}
}
%%% end \TestProcedure[6] test description container